Chatbots and messaging platforms in the classroom: an analysis from the teacher's perspective

### 2021-11-09 edubots_surveys.Rnw
Fixing reference to 7
Reference to Section 7 (Appendix I) is now clearer
Adding "i.e."
Addresing another comment

A total of 282 teachers responded to the survey: 193 teaching at the University
(68.4\%) and 89 at other tertiary education institutions (31.6\%). Survey
questions are shown in \ref{app:questions}.

@@

Group messaging apps have become a powerful tool for \textcolor{blue}{communicating} with
students. Also, many of them have built-in chatbots to enhance the learning
process. After an initial analysis to the answers to the first survey, we
realized that there were some prior issues mainly related to the adoption of a
technology, chatbots, that generally piggybacks on another, messaging
applications. In a technology adoption model, perceived ease of use and
perceived usefulness are essential. But it is going to be very difficult for
teachers to find {\em chatbots} easy to use if they, previously, do not
consider, or simply use, the messaging tools to which they are attached.

>>>>

A total of 282 teachers responded to the survey: 193 teaching at the University
(68.4\%) and 89 at other tertiary education institutions (31.6\%). Survey
questions are shown in Appendix I (Section \ref{app:questions}).

@@

Group messaging apps have become a powerful tool for \textcolor{blue}{communicating} with
students. Also, many of them have built-in chatbots to enhance the learning
process. After an initial analysis to the answers to the first survey, we
realized that there were some prior issues mainly related to the adoption of a
technology, i.e. chatbots, that generally piggybacks on another, i.e. messaging
applications. In a technology adoption model, perceived ease of use and
perceived usefulness are essential. But it is going to be very difficult for
teachers to find {\em chatbots} easy to use if they, previously, do not
consider, or simply use, the messaging tools to which they are attached.
